Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-12 thirdPaper/draft/typeConeAssociahedra.tex
workout presentation

\noindent
Let~$\Fan$ be an essential complete polyhedral fan in~$\R^n$ (all definitions are recalled in~\cref{ssec:polytopes and fans}).
The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P. McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parametrizes the set of all possible polytopal realizations of~$\Fan$. These realizations can be described explicitly as affine sections of the nonnegative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).  
If $\Fan$ is a simplicial fan and has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: The~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
We also completely describe the facets of the type cone for graph associahedra in~\cref{subsec:typeConeGA}, to which our strategy does not apply, as only the classical associahedron has a simplicial type cone.

@@

\noindent
We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix of finite type~$\B_\circ$. We provide the following polytopal realizations of~$\Fan(\B_\circ)$:

@@

Here, $\meshes$ represents the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$. By the unique exchange relation property, the~$\alpha_{x,x',y}$'s do not depend on the specific choice of the clusters~$X,X'$.

@@

\newtheorem*{coro:simplicialTypeConeCA}{\cref{coro:simplicialTypeConeCA}}
\begin{coro:simplicialTypeConeCA}
The type cone~$\typeCone(\Fan(\B_\circ))$ is simplicial.
\end{coro:simplicialTypeConeCA}

\para{Gentle algebras, non-kissing complex, generalized accordiohedra}
(\cref{subsec:typeConeNKC})

@@

Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sec:Kbproj}, by making use of representation theory, and state here the following consequence.

\newtheorem*{prop:exchangeablePairsNKC}{\cref{prop:exchangeablePairsNKC}\,(iv)}
\begin{prop:exchangeablePairsNKC}
The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
\end{prop:exchangeablePairsNKC}

\cref{subsubsec:simplicialTypeConeNKC} is dedicated to giving a purely combinatorial proof of the following statement.

\newtheorem*{coro:simplicialTypeConeNKC}{\cref{coro:simplicialTypeConeNKC}}
\begin{coro:simplicialTypeConeNKC}
Assume that the gentle bound quiver~$\quiver$ is brick and 2-acyclic.
Then the type cone~$\typeCone(\Fan(\quiver))$ is simplicial.
\end{coro:simplicialTypeConeNKC}

An alternative algebraic proof, using the main result of \cref{sec:extricats}, is given in \cref{sec:Kbproj}.

Combining these pieces, we make use of our type cone approach to deduce the following.

\newtheorem*{coro:allPolytopalRealizationsNKC}{\cref{coro:allPolytopalRealizationsNKC}}
\begin{coro:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{coro:allPolytopalRealizationsNKC}

Here, $\strings$ is the set of all strings of~$\quiver$, and~$\walks$ the set of all walks on~$\quiver$ (i.e. of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices). If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.

@@

Let~$\cat$ be a cluster category with finitely many isomorphism classes of indecomposable objects (see \cref{sec:setting} for the precise and more general setting in which the theorem is proven).
Let~$\Ksp(\cat)$ be the split Grothendieck group of~$\cat$.
Fix a cluster-tilting object~$T\in\cat$, and let~$K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles
$
X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X
$
with~$h \in (\susp T)$.
Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
For any indecomposable~$X\in\cat$, write~$\ell_X = [X]+[\susp^{-1}X]-[E]$, where~$E$ is the middle term of an almost split triangle starting at~$X$.
For any objects~$X,Y\in\cat$, we write~$\langle X, Y \rangle$ for~$\dim_\field\Hom{\Lambda}(FX,FY)$, where~$\Lambda$ is the cluster-tilted algebra~$\End{\cat}(T)$ and~$F$ is the equivalence of categories~$\cat(T,-):\cat/(\susp T) \to \MOD \Lambda$.

@@

The previous two statements also hold when~$T$ is an additive subcategory rather than a mere object.
Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
Then, with notations analogous to those used for cluster categories above, we obtain the following:

@@

Note that the family of brick and $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a brick and $2$-acyclic gentle quiver.
We will see in \cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in \cref{coro:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\begin{theorem}
\label{coro:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{theorem}

@@

\begin{remark}
\label{exm:nonSimplicialTypeConeNKC}
Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore \cref{coro:simplicialTypeConeNKC,coro:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
The right one is brick but is $2$-cyclic.

@@

\begin{notation}
We let~$\Modt$ denote the category of additive functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, i.e. cokernels of morphisms between representable functors.
We let~$F:\cat\to\Modt$ be the functor defined on objects by sending~$X\in\cat$ to~$\cat(-,X)|_\tc$.
\end{notation}

@@

\begin{remark}
\label{rem:equivalence Sigma}
For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
As noticed in \cref{lem:shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (i.e. such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
\[
\xy
(-12,6)*+{T}="0";
(0,6)*+{0}="2";
(12,6)*+{\susp T}="4";
(24,6)*+{}="6";
%
(-12,-6)*+{T'}="10";
(0,-6)*+{0}="12";
(12,-6)*+{\susp T'}="14";
(24,-6)*+{}="16";
%
{\ar "0";"2"};
{\ar "2";"4"};
{\ar@{-->}^{\eps_T} "4";"6"};
%
{\ar_{f} "0";"10"};
{\ar "2";"12"};
{\ar^{\susp f} "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
{\ar@{-->}_{\eps_{T'}} "14";"16"};
\endxy
\]
This gives an equivalence of additive categories
\[
 \susp: \tc \to \susp\tc
\]
where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are isomorphic to objects of the form~$\susp T$, for some~$T\in\tc$.
\end{remark}

@@

\begin{definition}
\label{def:mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (i.e. any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
\end{definition}

@@

\begin{proof}
Let~$\Lambda=\field Q / I$ be any gentle algebra of finite representation type, and let~$M$ be an indecomposable~$\Lambda$-module.
Write~$\sigma$ for the string corresponding to~$\tau M$.
Then the walks (i.e. the maximal strings in the blossoming bound quiver of~$(Q,I)$) associated with~$M$ and~$\tau M$ are respectively~$\omega_M = \hh\sigma = p^{-1}\alpha\sigma\beta^{-1}q$ and~$\omega_{\tau M}=\cc\sigma=p'\alpha'^{-1}\sigma\beta'q'^{-1}$, where~$p,p',q,q'$ are paths and~$\alpha,\alpha',\beta,\beta'$ are arrows in the blossoming quiver.

@@

\begin{proof}[Proof of \cref{coro:simplicialTypeConeNKCalgebraic}]
The unique exchange relation property follows from \cref{prop:exchange conflations are unique} (2).
By \cref{lem:characterization Gentle 2-acyclic}, the assumptions of \cref{thm:brick-algebra-condition} are satisfied.
We can thus apply \cref{thm:extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (i.e. the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
Hence the type cone of the support~$\tau$-tilting fan is simplicial.
\end{proof}

>>>>

\noindent
Let~$\Fan$ be an essential complete polyhedral fan in~$\R^n$ (all definitions are recalled in~\cref{ssec:polytopes and fans}).
The type cone~$\typeCone(\Fan)$ of~$\Fan$ (\cref{ssec:type cone}), introduced by P. McMullen~\cite{McMullen-typeCone}, is a polyhedral cone that parametrizes the set of all possible polytopal realizations of~$\Fan$. These realizations can be described explicitly as affine sections of the non-negative orthant~$\R^N_{\geq0}$, where~$N$ is the number of rays of~$\Fan$ (\cref{prop:alternativePolytopalRealization}).  
If $\Fan$ is a simplicial fan and has the unique exchange relation property (\cref{def:uerp}), then its type cone is easier to describe and study.
And if moreover the type cone~$\typeCone(\Fan)$ is simplicial (\cref{rem:dimTypeCone}), then all possible polytopal realizations of~$\Fan$ can be described explicitely in terms of~$N-n$ positive real parameters (\cref{coro:simplicialTypeCone}).
This gives a new point of view on~\cite{ArkaniHamedBaiHeYan,BazierMatteDouvilleMousavandThomasYildirim}, illustrated in \cref{subsec:typeConeAsso} for classical associahedra, that we then apply to two families of~$\b{g}$-vector fans generalizing the~$\b{g}$-vector fans of classical associahedra: the~$\b{g}$-vector fans of cluster algebras of finite type (generalized associahedra) in~\cref{subsec:typeConeCA}, and the~$\b{g}$-vector fans of gentle algebras (non-kissing associahedra, non-crossing associahedra, generalized accordiohedra) in~\cref{subsec:typeConeNKC}.
We also completely describe the facets of the type cone for graph associahedra in~\cref{subsec:typeConeGA}, to which our strategy does not apply, as only the classical associahedron has a simplicial type cone.

@@

\noindent
We first consider the~$\b{g}$-vector fan~$\Fan(\B_\circ)$ of a skew-symmetrizable cluster algebra of finite type, with respect to any initial exchange matrix~$\B_\circ$ (acyclic or not). We provide the following polytopal realizations of~$\Fan(\B_\circ)$.

@@

Here, $\meshes$ denotes the set of all pairs~$\{x,x'\}$ related by non-initial mesh mutations (\cref{def:meshMutation}), and~$\principalVariables$ the set of cluster variables.
For $\{x,x'\} \in \meshes$ and $y \in \principalVariables$, the coefficient $\alpha_{x,x',y}$ is defined as follows: $\alpha_{x,x',y}$ is set to be~$|b_{xy}|$ if~$y\in X\cap X'$ and $0$ otherwise, where~$X,X'$ are any two clusters such that~$X \ssm \{x\} = X' \ssm \{x'\}$. By the unique exchange relation property, the coefficients~$\alpha_{x,x',y}$ do not depend on the specific choice of clusters~$X,X'$.

@@

\newtheorem*{coro:simplicialTypeConeCA}{\cref{coro:simplicialTypeConeCA}}
\begin{coro:simplicialTypeConeCA}
The type cone~$\typeCone \big( \Fan(\B_\circ) \big)$ is simplicial.
\end{coro:simplicialTypeConeCA}

\para{Gentle algebras, non-kissing complexes, and generalized accordiohedra}
(\cref{subsec:typeConeNKC})

@@

Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called non-kissing fan.
We provide the following polytopal realizations of~$\Fan(\quiver)$.

\newtheorem*{thm:allPolytopalRealizationsNKC}{\cref{thm:allPolytopalRealizationsNKC}}
\begin{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{thm:allPolytopalRealizationsNKC}

Here, $\strings$ is the set of all strings of~$\quiver$, and~$\walks$ the set of all walks on~$\quiver$ (\ie of all strings of the blossoming bound quiver of~$\quiver$ that join two blossom vertices).
If~$\sigma$ is a string of~$\quiver$, we make use of the evocative notations~$\cc{\sigma}, \hh{\sigma}, \hc{\sigma}, \ch{\sigma}$ for the walks obtained by adding, in the blossoming bound quiver, hooks or cohooks at each end of~$\sigma$.

The two main ingredients are similar to those for cluster algebras.
As a first step, we obtain the following consequence of \cref{prop:exchangeablePairsNKC} (ii), which is proved in \cref{sec:Kbproj} by representation theory.

\newtheorem*{prop:exchangeablePairsNKC}{\cref{prop:exchangeablePairsNKC}\,{\normalfont (iv)}}
\begin{prop:exchangeablePairsNKC}
The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
\end{prop:exchangeablePairsNKC}

The second step is the following statement, for which we provide a purely combinatorial proof in \cref{subsubsec:simplicialTypeConeNKC} and an algebraic proof in \cref{sec:Kbproj}, using the main result of \cref{sec:extricats}.

\newtheorem*{coro:simplicialTypeConeNKC}{\cref{coro:simplicialTypeConeNKC}}
\begin{coro:simplicialTypeConeNKC}
If the gentle bound quiver~$\quiver$ is brick and 2-acyclic, then the type cone~$\typeCone \big( \Fan(\quiver) \big)$ is simplicial.
\end{coro:simplicialTypeConeNKC}

@@

Let~$\cat$ be a cluster category with finitely many isomorphism classes of indecomposable objects (see \cref{sec:setting} for the precise and more general setting in which the theorem is proven).
Let~$\Ksp(\cat)$ be the split Grothendieck group of~$\cat$.
Fix a cluster-tilting object~$T\in\cat$, and let $K_0(\cat ; T)$ be the quotient of~$\Ksp(\cat)$ by the relations~$[X]+[Z]-[Y]$ for all triangles ${X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X}$ with~$h \in (\susp T)$.
Denote by~$\b{g}:\Ksp(\cat) \to K_0(\cat ; T)$ the canonical projection.
For any indecomposable~$X\in\cat$, write~$\ell_X = [X]+[\susp^{-1}X]-[E]$, where~$E$ is the middle term of an almost split triangle starting at~$X$.
For any objects~$X,Y\in\cat$, we write~$\langle X, Y \rangle$ for~$\dim_\field\Hom{\Lambda}(FX,FY)$, where~$\Lambda$ is the cluster-tilted algebra~$\End{\cat}(T)$ and~$F$ is the equivalence of categories~$\cat(T,-):\cat/(\susp T) \to \MOD \Lambda$.

@@

The previous two statements also hold when~$T$ is an additive subcategory rather than a mere object.
Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
Then, with notations analogous to those used for cluster categories above, we obtain the following statement.

@@

Note that the family of brick and $2$-acyclic gentle quivers already contains a lot of relevant examples, including the gentle grid and dissection quivers discussed in \cref{subsubsec:nonkissingComplex}.
In particular, the classical associahedron is the gentle associahedron of a brick and $2$-acyclic gentle quiver.
We will see in \cref{coro:simplicialTypeConeNKC} that the type cone of the non-kissing fan~$\gvectorFan[\quiver]$ of a brick and $2$-acyclic gentle quiver~$\quiver$ happens to be simplicial, and we will derive in \cref{thm:allPolytopalRealizationsNKC} a simple description of all polytopal realizations of~$\gvectorFan[\quiver]$.

@@

\begin{theorem}
\label{thm:allPolytopalRealizationsNKC}
For any brick and $2$-acyclic gentle quiver~$\quiver$ and any~$\b{\ell} \in \R_{>0}^{\strings}$, the polytope
\[
R_\b{\ell}(\quiver) \eqdef \set{\b{z} \in \R^{\walks}}{\begin{array}{l} \b{z} \ge 0 \qquad\text{and}\qquad \b{z}_\omega = 0 \text{ for any improper walk } \omega \\ \b{z}_{\cc{\sigma}} + \b{z}_{\hh{\sigma}} - \b{z}_{\hc{\sigma}} - \b{z}_{\ch{\sigma}} = \b{\ell}_\sigma \text{ for all } \sigma \in \strings\end{array}}
\]
is a realization of the non-kissing fan~$\gvectorFan[\quiver]$.
Moreover, the polytopes~$R_\b{\ell}(\quiver)$ for~$\b{\ell} \in \R_{>0}^{\strings}$ describe all polytopal realizations of~$\gvectorFan[\quiver]$.
\end{theorem}

@@

\begin{remark}
\label{exm:nonSimplicialTypeConeNKC}
Note that \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and therefore \cref{coro:simplicialTypeConeNKC,thm:allPolytopalRealizationsNKC} fail when the quiver is not brick or $2$-cyclic.
The smallest exemples are the $2$-cycles whose non-kissing fans are represented in \cref{fig:nonkissingFans2}.
The left one is not brick: it has a non-distinguishable string and a self-kissing walk.
The right one is brick but is $2$-cyclic.

@@

\begin{notation}
We let~$\Modt$ denote the category of additive functors from~$\tc$ to Abelian groups, and~$\modt$ its full subcategory of functors that are finitely presented, \ie cokernels of morphisms between representable functors.
We let~$F:\cat\to\Modt$ be the functor defined on objects by sending~$X\in\cat$ to~$\cat(-,X)|_\tc$.
\end{notation}

@@

\begin{remark}
\label{rem:equivalence Sigma}
For any~$T\in\tc$, fix an extriangle~$T\infl 0\defl\susp T\overset{\eps_T}{\dashrightarrow}$.
As noticed in \cref{lem:shifts of extriangles}, for any morphism~$T\overset{f}{\to}T'$ in~$\tc$, there is a unique morphism~$\susp f\in\cat(\susp T,\susp T')$ such that~${f_\ast\eps_T=(\susp f)^\ast\eps_{T'}}$ (\ie such that~$(f,\susp f)$ is a morphism from~$\eps_T$ to~$\eps_{T'}$), as illustrated below:
\[
\xy
(-12,6)*+{T}="0";
(0,6)*+{0}="2";
(12,6)*+{\susp T}="4";
(24,6)*+{}="6";
%
(-12,-6)*+{T'}="10";
(0,-6)*+{0}="12";
(12,-6)*+{\susp T'}="14";
(24,-6)*+{}="16";
%
{\ar "0";"2"};
{\ar "2";"4"};
{\ar@{-->}^{\eps_T} "4";"6"};
%
{\ar_{f} "0";"10"};
{\ar "2";"12"};
{\ar^{\susp f} "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
{\ar@{-->}_{\eps_{T'}} "14";"16"};
\endxy
\]
This gives an equivalence of additive categories
\[
 \susp: \tc \to \susp\tc
\]
where~$\susp\tc$ is the full subcategory of~$\cat$ whose objects are isomorphic to objects of the form~$\susp T$, for some~$T\in\tc$.
\end{remark}

@@

\begin{definition}
\label{def:mutation conflation}
A conflation $X\infl E\defl Y$ of~$K^{[-1,0]}(\proj \Lambda)$ is called a \defn{mutation conflation} if there are basic, two-term, silting objects $X\oplus R$, $Y\oplus R$, with~$X$ and~$Y$ indecomposable, such that the inflation $X\infl E$ is a left ($\add R$)-approximation (\ie any morphism from~$X$ to an object in~$\add R$ factors through~$X\infl E$).
\end{definition}

@@

\begin{proof}
Let~$\Lambda=\field Q / I$ be any gentle algebra of finite representation type, and let~$M$ be an indecomposable~$\Lambda$-module.
Write~$\sigma$ for the string corresponding to~$\tau M$.
Then the walks (\ie the maximal strings in the blossoming bound quiver of~$(Q,I)$) associated with~$M$ and~$\tau M$ are respectively~$\omega_M = \hh\sigma = p^{-1}\alpha\sigma\beta^{-1}q$ and~$\omega_{\tau M}=\cc\sigma=p'\alpha'^{-1}\sigma\beta'q'^{-1}$, where~$p,p',q,q'$ are paths and~$\alpha,\alpha',\beta,\beta'$ are arrows in the blossoming quiver.

@@

\begin{proof}[Proof of \cref{coro:simplicialTypeConeNKCalgebraic}]
The unique exchange relation property follows from \cref{prop:exchange conflations are unique} (2).
By \cref{lem:characterization Gentle 2-acyclic}, the assumptions of \cref{thm:brick-algebra-condition} are satisfied.
We can thus apply \cref{thm:extricats} and its corollary, which shows that there is the same number of extremal exchange pairs of the support~$\tau$-tilting fan (\ie the non-kissing fan) as there are meshes in the Auslander--Reiten quiver of~$\Lambda$.
Hence the type cone of the support~$\tau$-tilting fan is simplicial.
\end{proof}
